Manuscript progress report

### 2024-02-02 Docs/manuscript.Rmd
rotated figures and tables

library(here)
library(tidyverse)
library(ggpubr)
library(refund)
library(lme4)
library(ROCR)
library(GLMMadaptive)
library(kableExtra)
library(knitr)
library(mvtnorm)
library(mgcv)
library(splines)
library(boot)
theme_set(theme_minimal())

## prediction window 
window <- seq(0, 1, by = 0.2)
M <- 500
```

@@

@@

```{r}
# range(pred_list_all[[1]]$pred0.2, na.rm = T)
fig_fgfpca <- pred_list_all[[1]] %>%
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, pred0.2, pred0.4, pred0.6, pred0.8), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id, nrow = 1)+
  labs(title = "fGFPCA", col = "Maximum observation time", x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))

fig_adglmm <- pred_list_ref[[1]] %>%
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, pred0.2, pred0.4, pred0.6, pred0.8), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id, nrow = 1)+
  labs(title = "GLMMadaptive", col = "Maximum observation time", 
       x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))

fig_gfosr_l1 <- pred_list_gfosr_l1[[1]] %>%
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, pred_w1, pred_w2, pred_w3, pred_w4), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred_w1, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w2, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w3, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w4, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id, nrow = 1)+
  labs(title = "GFOSR (L=1)", col = "Maximum observation time",
       x="Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))

fig_gfosr_l5 <- pred_list_gfosr_l5[[1]] %>%
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, pred_w1, pred_w2, pred_w3, pred_w4), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred_w1, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w2, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w3, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w4, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id, nrow = 1)+
  labs(title = "GFOSR (L=5)", col = "Maximum observation time",
       x="Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))

```{r fig_sim, fig.height=8, fig.width=8}
ggarrange(fig_fgfpca, fig_adglmm, fig_gfosr_l1, fig_gfosr_l5,
          ncol = 1, common.legend = T)
```

## ISE

```{r}
## ISE container 
ise_fgfpca <- ise_adglmm <- ise_gfosr_l1 <- ise_gfosr_l5 <- 
  array(NA, dim = c(length(window)-2, length(window)-2, M))
# dims: prediction window, max obs time, simulation iter

@@

```{r}
rbind(mean_ise_fgfpca, mean_ise_adglmm, 
           mean_ise_gfosr_l1, mean_ise_gfosr_l5) %>%
  as_tibble() %>%
  mutate(Window = rep(c("(0.2, 0.4]", "(0.4, 0.6]", 
                        "(0.6, 0.8]", "(0.8, 1.0]"), 4),
         .before=1) %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F) %>% 
  group_rows(index = c("fGFPCA" = 4, "GLMMadaptive" = 4,
                     "GFOSR (L=1)" = 4, "GFOSR (L=5)" = 4)) %>%
  add_header_above(c(" "= 1, "Maximum observation time" = 4))
```

@@

```{r}
rbind(mean_auc_fgfpca, mean_auc_adglmm, 
           mean_auc_gfosr_l1, mean_auc_gfosr_l5) %>%
  as_tibble() %>%
  mutate(Window = rep(c("(0.2, 0.4]", "(0.4, 0.6]", 
                        "(0.6, 0.8]", "(0.8, 1.0]"), 4),
         .before=1) %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F) %>% 
  group_rows(index = c("fGFPCA" = 4, "GLMMadaptive" = 4,
                     "GFOSR (L=1)" = 4, "GFOSR (L=5)" = 4)) %>%
  add_header_above(c(" "= 1, "Maximum observation time" = 4))
```

@@

```{r fig_pred_subset}
fig_fgfpca2 <- pred_subset_fGFPCA[[1]] %>%
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id, nrow = 1)+
  labs(title = "fGFPCA", col = "Maximum observation time",
       x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))

fig_adglmm2 <- pred_subset_adglmm[[1]] %>% 
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id, nrow = 1)+
  labs(title = "GLMMadaptive", col = "Maximum observation time",
       x = "Time", y = "")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))

fig_gfosr_l1_2 <- pred_subset_gfosr_l1[[1]] %>% 
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred_w1, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w2, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w3, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w4, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id, nrow=1)+
  labs(title = "GFOSR (L=1)", col = "Maximum observation time",
       x = "Time", y = "")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))

fig_gfosr_l5_2 <- pred_subset_gfosr_l5[[1]] %>% 
  filter(id %in% rand_id) %>%
  mutate_at(vars(eta_i, starts_with("pred")), function(x){exp(x)/(1+exp(x))}) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred_w1, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w2, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w3, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred_w4, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_wrap(~id, nrow=1)+
  labs(title = "GFOSR (L=5)", col = "Maximum observation time",
       x = "Time", y = "")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(axis.text = element_text(size = 5), 
        title = element_text(size = 8))
```

```{r fig_sim2, fig.height=8, fig.width=8}
ggarrange(fig_fgfpca2, fig_adglmm2, fig_gfosr_l1_2, fig_gfosr_l5_2,
          ncol = 1, common.legend = T)
```

## ISE

```{r}
## ISE container 
ise_fgfpca2 <- ise_adglmm2 <- ise_gfosr_l1_2 <- ise_gfosr_l5_2 <- 
  array(NA, dim = c(length(window)-2, length(window)-2, M))
# dims: prediction window, max obs time, simulation iter

@@

```{r}
rbind(mean_ise_fgfpca2, mean_ise_adglmm2, 
           mean_ise_gfosr_l1_2, mean_ise_gfosr_l5_2) %>%
  as_tibble() %>%
  mutate(Window = rep(c("(0.2, 0.4]", "(0.4, 0.6]", 
                        "(0.6, 0.8]", "(0.8, 1.0]"), 4),
         .before=1) %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F) %>% 
  group_rows(index = c("fGFPCA" = 4, "GLMMadaptive" = 4,
                     "GFOSR (L=1)" = 4, "GFOSR (L=5)" = 4)) %>%
  add_header_above(c(" "= 1, "Maximum observation time" = 4))
```

```{r}
## auc container 
auc_fgfpca2 <- auc_adglmm2 <- auc_gfosr_l1_2 <- auc_gfosr_l5_2 <- 
  array(NA, dim = c(length(window)-2, length(window)-2, M))
```

@@

```{r}
rbind(mean_auc_fgfpca2, mean_auc_adglmm2, 
           mean_auc_gfosr_l1_2, mean_auc_gfosr_l5_2) %>%
  as_tibble() %>%
  mutate(Window = rep(c("(0.2, 0.4]", "(0.4, 0.6]", 
                        "(0.6, 0.8]", "(0.8, 1.0]"), 4),
         .before=1) %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F) %>% 
  group_rows(index = c("fGFPCA" = 4, "GLMMadaptive" = 4,
                     "GFOSR (L=1)" = 4, "GFOSR (L=5)" = 4)) %>%
  add_header_above(c(" "= 1, "Maximum observation time" = 4))
```

@@

```{r load_nhanes}
df_nhanes <- read_rds(here("Data/nhanes_bi.rds"))
load(here("Data/ApplOutput.RData"))
```

```{r nhance_example}
df_nhanes %>% select(SEQN, Z, sind) %>% 
  filter(SEQN %in% unique(nhanes_pred_adglmm$id) | SEQN %in% unique(nhanes_pred_fgfpca$id)) %>%
  mutate(Z = factor(Z, levels = 0:1, labels = c("Inactive", "Active"))) %>%
  mutate(SEQN = factor(SEQN)) %>%
  ggplot()+
  geom_tile(aes(x=sind, y = SEQN, fill = Z))+
  labs(x="Time", y="Subject", title = "Overview of NHANES binary activity indicator")+
  theme(axis.text.y = element_blank())+
  scale_x_continuous(breaks = seq(0, 1440, by = 480),
                     labels = c("Midnight", "8am", "4pm", "Midnight"))
```

@@

```{r auc_fGFPCA_nhanes}
window3 <- c(0, 480, 960, 1440)

@@

```{r auc_GLMMadaptive_nhanes}
auc_mat_nhanes2 <- nhanes_pred_adglmm %>%
  mutate(window = cut(t, breaks = window3, include.lowest = T)) %>% 
  select(Y, starts_with("pred"), window) %>%
  group_by(window) %>%
  summarise(auc1 = get_auc(Y, pred480),
            auc2 = get_auc(Y, pred960)) %>%
  filter(window != "[0,480]") %>% 
  select(starts_with("auc"))

@@

```{r}
data.frame(Window = c("8am-4pm", "4am-midnight"),
           auc_mat_nhanes, auc_mat_nhanes2, check.names = F) %>%
  kable(digits = 3, caption = "Area Under the ROC curve", booktabs = T) %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" "=1, "fGFPCA" = 2, "GLMMadaptive" = 2)) %>%
  add_header_above(c(" "= 1, "Maximum observation time" = 4))
```

@@

```{r pred_nhanes, fig.height=4, fig.width=10}
rand_id3 <- sample(unique(nhanes_pred_fgfpca$id), 4)

>>>>

library(here)
library(tidyverse)
library(ggpubr)
library(refund)
library(lme4)
library(ROCR)
library(GLMMadaptive)
library(kableExtra)
library(knitr)
library(mvtnorm)
library(mgcv)
library(splines)
library(boot)

# plot settings
theme_set(theme_minimal())
cols <- c("0.2"= "#FDCC8A", "0.4"="#FC8D59", "0.6"="#E34A33", "0.8"="#B30000", "True"="#000000")
# brewer.pal(5, "OrRd")

# define a color palette 
## prediction window 
window <- seq(0, 1, by = 0.2)
M <- 500

@@

## Figures

@@

```{r fig_large_sim, fig.height=8, fig.width=8}
bind_rows(
  pred_list_all[[1]] %>% filter(id %in% rand_id) %>% 
    mutate(method="fGFPCA"),
  pred_list_ref[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GLMMadaptive"),
  pred_list_gfosr_l1[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GFOSR (L=1)") %>%
    rename(pred0.2=pred_w1, pred0.4=pred_w2, pred0.6=pred_w3, pred0.8=pred_w4),
  pred_list_gfosr_l5[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GFOSR (L=5)") %>%
    rename(pred0.2=pred_w1, pred0.4=pred_w2, pred0.6=pred_w3, pred0.8=pred_w4)
) %>% mutate_at(vars(eta_i, pred0.2, pred0.4, pred0.6, pred0.8), 
                .funs = function(x){exp(x)/(1+exp(x))}) %>%
  mutate(method=factor(method, 
         levels = c("fGFPCA", "GFOSR (L=5)", "GFOSR (L=1)","GLMMadaptive"))) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_grid(rows = vars(id), cols = vars(method))+
  labs(col = "Maximum observation time", x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(legend.position = "bottom")+
  scale_color_manual(values = cols)
```

## ISE and AUC

```{r ise}
## ISE container 
ise_fgfpca <- ise_adglmm <- ise_gfosr_l1 <- ise_gfosr_l5 <- 
  array(NA, dim = c(length(window)-2, length(window)-2, M))
# dims: prediction window, max obs time, simulation iter

@@

@@

```{r table_sim1}
fgfpca1 <- rbind(mean_ise_fgfpca ,mean_auc_fgfpca) %>% as_tibble() %>%
  mutate(Window = rep(c("(0.2, 0.4]", "(0.4, 0.6]", "(0.6, 0.8]", "(0.8, 1.0]"), 2), .before=1)
gfosr_l5_1 <- rbind(mean_ise_gfosr_l5 ,mean_auc_gfosr_l5) %>% as_tibble()
gfosr_l1_1 <- rbind(mean_ise_gfosr_l1 ,mean_auc_gfosr_l1) %>% as_tibble()
adglmm1 <- rbind(mean_ise_adglmm ,mean_auc_adglmm) %>% as_tibble()

bind_cols(fgfpca1, gfosr_l5_1, gfosr_l1_1, adglmm1, .name_repair = "minimal") %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "fGFPCA" = 4, "GFOSR (L=5)" = 4, 
                     "GFOSR (L=1)" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" " = 1, "Maximum observation time" = 16)) %>%
  group_rows(index = c("ISE"= 4, "AUC" = 4))

@@

```{r fig_small_sim, fig.height=8, fig.width=8}
bind_rows(
  pred_subset_fGFPCA[[1]] %>% filter(id %in% rand_id) %>% mutate(method="fGFPCA"),
  pred_subset_gfosr_l5[[1]] %>% filter(id %in% rand_id) %>% mutate(method = "GFOSR (L=5)") %>% 
    rename(pred0.2=pred_w1, pred0.4=pred_w2, pred0.6=pred_w3, pred0.8=pred_w4),
  pred_subset_gfosr_l1[[1]] %>% filter(id %in% rand_id) %>% mutate(method = "GFOSR (L=1)") %>%
    rename(pred0.2=pred_w1, pred0.4=pred_w2, pred0.6=pred_w3, pred0.8=pred_w4),
  pred_subset_adglmm[[1]] %>% filter(id %in% rand_id) %>% mutate(method = "GLMMadaptive")) %>%
  mutate_at(vars(eta_i, pred0.2, pred0.4, pred0.6, pred0.8), 
                .funs = function(x){exp(x)/(1+exp(x))}) %>%
  mutate(method=factor(method, 
         levels = c("fGFPCA", "GFOSR (L=5)", "GFOSR (L=1)","GLMMadaptive"))) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), linetype="dashed", na.rm=T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), linetype="dashed", na.rm=T)+
  facet_grid(rows = vars(id), cols = vars(method))+
  labs(col = "Maximum observation time", x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(legend.position = "bottom")+
  scale_color_manual(values = cols)
```

## ISE and AUC

```{r ise_subset}
## ISE container 
ise_fgfpca2 <- ise_adglmm2 <- ise_gfosr_l1_2 <- ise_gfosr_l5_2 <- 
  array(NA, dim = c(length(window)-2, length(window)-2, M))
# dims: prediction window, max obs time, simulation iter

@@

```{r auc2}
## auc container 
auc_fgfpca2 <- auc_adglmm2 <- auc_gfosr_l1_2 <- auc_gfosr_l5_2 <- 
  array(NA, dim = c(length(window)-2, length(window)-2, M))
```

@@

```{r table_sim2}
fgfpca2 <- rbind(mean_ise_fgfpca2 ,mean_auc_fgfpca2) %>% as_tibble() %>%
  mutate(Window = rep(c("(0.2, 0.4]", "(0.4, 0.6]", "(0.6, 0.8]", "(0.8, 1.0]"), 2), .before=1)
gfosr_l5_2 <- rbind(mean_ise_gfosr_l5_2 ,mean_auc_gfosr_l5_2) %>% as_tibble()
gfosr_l1_2 <- rbind(mean_ise_gfosr_l1_2 ,mean_auc_gfosr_l1_2) %>% as_tibble()
adglmm2 <- rbind(mean_ise_adglmm2 ,mean_auc_adglmm2) %>% as_tibble()

bind_cols(fgfpca2, gfosr_l5_2, gfosr_l1_2, adglmm2, .name_repair = "minimal") %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "fGFPCA" = 4, "GFOSR (L=5)" = 4, 
                     "GFOSR (L=1)" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" " = 1, "Maximum observation time" = 16)) %>%
  group_rows(index = c("ISE"= 4, "AUC" = 4))

@@

```{r load_nhanes, eval=FALSE}
df_nhanes <- read_rds(here("Data/nhanes_bi.rds"))
load(here("Data/ApplOutput.RData"))
```

```{r nhance_example, eval=FALSE}
df_nhanes %>% select(SEQN, Z, sind) %>% 
  filter(SEQN %in% unique(nhanes_pred_adglmm$id) | SEQN %in% unique(nhanes_pred_fgfpca$id)) %>%
  mutate(Z = factor(Z, levels = 0:1, labels = c("Inactive", "Active"))) %>%
  mutate(SEQN = factor(SEQN)) %>%
  ggplot()+
  geom_tile(aes(x=sind, y = SEQN, fill = Z))+
  labs(x="Time", y="Subject", title = "Overview of NHANES binary activity indicator")+
  theme(axis.text.y = element_blank())+
  scale_x_continuous(breaks = seq(0, 1440, by = 480),
                     labels = c("Midnight", "8am", "4pm", "Midnight"))
```

@@

```{r auc_fGFPCA_nhanes, eval=FALSE}
window3 <- c(0, 480, 960, 1440)

@@

```{r auc_GLMMadaptive_nhanes, eval=FALSE}
auc_mat_nhanes2 <- nhanes_pred_adglmm %>%
  mutate(window = cut(t, breaks = window3, include.lowest = T)) %>% 
  select(Y, starts_with("pred"), window) %>%
  group_by(window) %>%
  summarise(auc1 = get_auc(Y, pred480),
            auc2 = get_auc(Y, pred960)) %>%
  filter(window != "[0,480]") %>% 
  select(starts_with("auc"))

@@

```{r, eval=FALSE}
data.frame(Window = c("8am-4pm", "4am-midnight"),
           auc_mat_nhanes, auc_mat_nhanes2, check.names = F) %>%
  kable(digits = 3, caption = "Area Under the ROC curve", booktabs = T) %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" "=1, "fGFPCA" = 2, "GLMMadaptive" = 2)) %>%
  add_header_above(c(" "= 1, "Maximum observation time" = 4))
```

@@

```{r pred_nhanes, fig.height=4, fig.width=10, eval=FALSE}
rand_id3 <- sample(unique(nhanes_pred_fgfpca$id), 4)
